A mechanization of semi-simplicial and semi-cubical sets in the calculus of inductive constructions

### 2022-11-09 paper/paper.tex
paper: minor additions

So far, we haven't paid attention to the fact that each addition of a layer has to be glued onto the border of the previous layer. So, each $\layer[n][p]$ has to depend on $\layer[n][p - 1]$. We also need a way to characterize the border of a filler of a layer, and this is $\restrf[n][p][\epsilon]$, for all $\epsilon < \nu$. For instance, the left $\filler[2][1]$ needs to glue onto the left borders of the two blue boxes $c_{\textsf{front}}$ and $c_{\textsf{back}}$, extracted as $\restrf[2][1][L](D)(d_\textsf{front})$ and $\restrf[2][1][L](D)(d_\textsf{back})$, where $d_\textsf{front}$ and $d_\textsf{back}$ are the underlying fullframes in $c_\textsf{front}$ $c_\textsf{back}$.

>>>>

So far, we haven't paid attention to the fact that each addition of a layer has to be glued onto the border of the previous layer. So, each $\layer[n][p]$ has to depend on $\layer[n][p - 1]$. We also need a way to characterize the border of a filler of a layer, and this is $\restrf[n][p][\epsilon]$, for all $\epsilon < \nu$. For instance, the left $\filler[2][1]$ needs to glue onto the left borders of the two blue boxes, and hence needs to depend on some $\framep[2][1]$. The borders of the two blue boxes are extracted as $\restrf[2][1][L](D)(d_\textsf{front})$ and $\restrf[2][1][L](D)(d_\textsf{back})$, where $d_\textsf{front}$ and $d_\textsf{back}$ are the inhabitants of $\framep[2][1](D)$.
